Nested sampling with two objective functions

### 2016-01-07 Paper/ms.tex
New references

\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

@@

Subject to the constraint $L_1(\xx) > L_1^*$, standard NS can continue but
attempting to increase $L_2$ instead of $L_1$. This is what we mean by
`turning the corner'. After $M_2$ such iterations,
the algorithm would have compressed the prior by a factor
$e^{(M_1 + M_2)/N}$ and therefore ended at a point in the $(L_1, L_2)$ plane
where $X(L_1, L_2) \approx e^{-(M_1 + M_2)/N}$. Any such run consisting of
$M_1 + M_2$ iterations will therefore appoximately finish on a contour line
of the function $X(L_1, L_2)$.

@@

@@

>>>>

\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{natbib}

@@

Subject to the constraint $L_1(\xx) > L_1^*$, standard NS can continue but
attempting to increase $L_2$ instead of $L_1$. This is what we mean by
`turning the corner'. After $M_2$ such iterations,
the algorithm would have compressed the prior by a factor
$e^{(M_1 + M_2)/N}$ and therefore ended at a point in the $(L_1, L_2)$ plane
where $X(L_1, L_2) \approx e^{-(M_1 + M_2)/N}$. Any such run consisting of
$M_1 + M_2$ iterations will therefore appoximately finish on a contour line
of the function $X(L_1, L_2)$.
We have explored the idea of using multiple turn-the-corner runs, with
the corner being turned at different times (i.e. using different values of
$M_1$), and combining the results using biased sampling
\citep{vardi, cameron} in order to estimate $Z(\beta_1, \beta_2)$. However,
this was very computationally intensive. We presented the turn-the-corner idea
here in order to provide an intuitive rationale for our actual algorithm given in
Section~\ref{sec:algorithm}.

@@

\bibitem[Cameron and Pettitt(2014)]{cameron} Cameron, E., and Pettitt, A., 2014,
``Recursive pathways to marginal likelihood estimation with
prior-sensitivity analysis.'' Statistical Science 29.3 (2014): 397-419.

@@

\bibitem[Vardi (1985)]{vardi}
Vardi, Yehuda. ``Empirical distributions in selection bias models.'', The Annals of Statistics (1985): 178-203.
